Extracting The Power of Dependent Types

### 2021-07-11 paper.tex
Adjusting sections 3 and 4.
Add paragraph on other languages we did this for

@@

\section{Scaling to Bigger Languages} \label{sec:scaling}
Not sure whether this deserves a separate section, but we need to explain
that the proposed technology perfectly scales to the level of bigger (more complex)
languages.

@@

>>>>

\todo[inline]{Move it somewhere}
This picture has been generated by the code that was extracted from our
Agda embedding.

\begin{center}
\epsfbox[0 0 64 64]{sierp.ps}
\end{center}

@@

@@

\paragraph{Scaling to bigger languages}

The main goal of this paper is to demonstrate how to define a
embedding and extractor using dependent types and reflection on a
small but complete example. In addition to the PostScript embedding
discussed in this paper, we applied our approach to several other
languages:
\begin{itemize}
\item Kaleidoscope, a minimalist imperative language used in the
  documentation of LLVM.
\item SaC (Single assignment C), a high-performance array language
  that generates efficient code for various architectures.
\item APL (Array Programming Language), another array language with
  heavily overloaded syntax that pioneered the concept of rank- and
  shape-polymorphic programming.
\end{itemize}
In addition, we used the embedding of APL to implement a Convolutional
Neural Network, and ensure that all the array instructions operate on
arrays of the correct dimensions. For more details on these examples,
refer to \citet{DBLP:journals/corr/abs-2105-10819}.

\paragraph{Future work}
